Icon Generation with Conditional Generative Adversarial Networks

### 2023-01-08 paper/src/sections/introduction.tex
LaTeX IntelliJ project

\subsection{Objective}\label{subsec:objective}
Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
To do this, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat'' or ``bird''.

>>>>

\subsection{Objective}\label{subsec:objective}
Using cGANs, it is possible to generate icons with specific characteristics or properties, given a public dataset such as Icons-50.
To do so, the cGAN would be trained on said dataset, with the conditioning variable being the desired label of the generated icons, in this case represented by an integer value corresponding to a class of icons, such ``cat'' or ``bird''.
\footnote{Source code and trained models are available at   \url{https://github.com/Necas209/Icon-Generation-cGANs}}

### 2023-01-08 paper/src/sections/results.tex
LaTeX IntelliJ project

@@

The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock} .

>>>>

The second model performed much better on this task, capturing finer details such as the correct color, and the hour and minutes hands, as it is clear from Fig.~\ref{fig:Icons10Clock}.

@@
